Composing Secure Compilers

### 2021-10-28 prisc.tex
Fix minor typo

\begin{definition}[Secure Instrumentation for Preserving $\cC$]\label{def:secure-instrumentation}
  A secure instrumentation with respect to some class $\cC$ is a pass that enforces hyperproperties described by some other class $\cC'$ without violating $\cC$-satisfying programs.
  We denote such a secure instrumentation as: $\sinstr{\stcomp{\bullet}}{\cC'}{\cC}$.
\end{definition}
Using this, we firstly want to inspect an compilation pipeline from memory-safe $\src{Rust}$ to optimised, insecure $\irl{C}$, to memory-safe $\trg{CheckedC}$.
Intuitively, we want to be able to state that this pipeline preserves memory safety, despite the fact that the pass to $\irl{C}$ does not.
% We want to be able to reconstruct memory safety for $\trg{CheckedC}$ despite the fact that $\irl{C}$ did not have it.
\begin{example}[Enforcement may preserve...]
  Given classes $\cC_{1}, \cC_{2}$ (resp. no property and memory safety, in our $\src{Rust}$ to $\trg{CheckedC}$ example) and compilers $\sicomp{\bullet}$,$\itcomp{\bullet}$, if:

>>>>

\begin{definition}[Secure Instrumentation for Preserving $\cC$]\label{def:secure-instrumentation}
  A secure instrumentation with respect to some class $\cC$ is a pass that enforces hyperproperties described by some other class $\cC'$ without violating $\cC$-satisfying programs.
  We denote such a secure instrumentation as: $\sinstr{\stcomp{\bullet}}{\cC'}{\cC}$.
\end{definition}
Using this, we firstly want to inspect a compilation pipeline from memory-safe $\src{Rust}$ to optimised, insecure $\irl{C}$, to memory-safe $\trg{CheckedC}$.
Intuitively, we want to be able to state that this pipeline preserves memory safety, despite the fact that the pass to $\irl{C}$ does not.
% We want to be able to reconstruct memory safety for $\trg{CheckedC}$ despite the fact that $\irl{C}$ did not have it.
\begin{example}[Enforcement may preserve...]
  Given classes $\cC_{1}, \cC_{2}$ (resp. no property and memory safety, in our $\src{Rust}$ to $\trg{CheckedC}$ example) and compilers $\sicomp{\bullet}$,$\itcomp{\bullet}$, if:
